\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-09-24 problem-formulation.tex
Minor

Now, let $\sigma_f^2 \defeq \E[\frac{f'(X)^2}{f(X)^2}]$ be the Fisher
information for the location in the family $\{P_\theta\}$, which is finite
when $f$ is log-concave and symmetric. We give particular attention to the
asymptotic relative efficiency (ARE) of estimators with respect to
asymptotically normal efficient estimators achieving the information
bound~\cite{VanDerVaart98}. In this case,
if $\{m(n), n \in \N\}$ is a sequence such that
\begin{equation*}
  \sqrt{m(n)} (\theta_n - \theta) \cd \normal(0, \sigma_f^2),
\end{equation*}
then the ARE of the estimator is~\cite[Def.~6.6.6]{LehmannCa98}
\begin{equation*}
  \ARE({\theta}_n) \defeq
  \liminf_{n\rightarrow \infty} \frac{m(n)}{n}.
\end{equation*}
In the special case where there exists $V \in \mathbb R$ such that
\[
m(n) R_n =
m(n) \mathbb E_\theta\left({\theta}_n - \theta \right)^2 = V + o(1),
\]
the ARE of ${\theta}_n$ is $\sigma_f^2/V$, so that $\theta_n$ requires a
sample $V / \sigma_f^2$-times larger than that of an efficient estimator for
comparable accuracy to the (information) efficient estimator.

@@

In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
\begin{equation} \label{eq:eta_def}
\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
\end{equation}
where the last equality is due to symmetry of $f(x)$. We note that 
\begin{equation}
\label{eq:eta_h}
\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
\end{equation}
where 
\[
h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\]
is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
%
For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
%
In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
\begin{assump} \label{assump:failure_rate}
 $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
\end{assump}
%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
Under this assumption we have, 
\[
4f^2(x) \leq \eta(x) \leq \eta(0),
\] 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median. Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$. \par
%
Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions). Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par

>>>>

Now, let $\sigma_f^2 \defeq \E[\frac{f'(X)^2}{f(X)^2}]$ be the Fisher
information for the location in the family $\{P_\theta\}$, which is finite
when $f$ is log-concave and symmetric. We give particular attention to the
asymptotic relative efficiency (ARE) of estimators with respect to
asymptotically normal efficient estimators achieving the information
bound~\cite{VanDerVaart98}. In this case,
if $\{m(n), n \in \N\}$ is a sequence such that
\begin{equation*}
  \sqrt{m(n)} (\theta_n - \theta) \cd \normal(0, \sigma_f^2),
\end{equation*}
then the ARE of the estimator is~\cite[Def.~6.6.6]{LehmannCa98}
\begin{equation*}
  \ARE({\theta}_n) \defeq
  \liminf_{n\rightarrow \infty} \frac{m(n)}{n}.
\end{equation*}
In the special case where there exists $V \in \mathbb R$ such that
\begin{equation*}
m(n) R_n =
m(n) \mathbb E_\theta\left({\theta}_n - \theta \right)^2 = V + o(1),
\end{equation*}
the ARE of ${\theta}_n$ is $\sigma_f^2/V$, so that $\theta_n$ requires a
sample $V / \sigma_f^2$-times larger than that of an efficient estimator for
comparable accuracy to the (information) efficient estimator.

@@

In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
\begin{equation} \label{eq:eta_def}
\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
\end{equation}
where the last equality is due to symmetry of $f(x)$. We note that 
\begin{equation}
\label{eq:eta_h}
\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
\end{equation}
where 
\begin{equation*}
h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\end{equation*}
is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
%
For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
%
In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
\begin{assump} \label{assump:failure_rate}
 $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
\end{assump}
%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
Under this assumption we have, 
\begin{equation*}
4f^2(x) \leq \eta(x) \leq \eta(0),
\end{equation*} 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median. Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$. \par
%
Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions). Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
